---
title: "disabled students & chronic absenteeism"
author: "Ellie "hacker(wo)man supreme" Heffernan"
date: "10/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Load in the data & load packages you will need. 
```{r}
library(readr)
library(lubridate)
library(tidyverse)
library(stringr)
library(ggplot2)
chronic_absenteeism <- read_csv("chronic_absenteeism.csv")
View(chronic_absenteeism)

```


#The Agency code's first three digits refer to the school district. The second three refer to the school itself. I want to create a new column that will just show what district the school is. I will use stringr to split the agency_code column in two & make a new column 

```{r}
chronic_absenteeism <-chronic_absenteeism %>% mutate(district_code = str_sub(chronic_absenteeism$agency_code,1,3))
  
  
```


#KC Elander recommended we remove all schools with percentages greater than 100, all charter schools, and all alternative schools.These schools enroll students later in the year, but they take their "count" data earlier. This is why they may have 400 chronically absent students and only 200 students enrolled. Many of those 400 students may have enrolled later. The data is flawed in this sense, and we should mention it in the story.  Phew. Time for some data cleaning.
```{r}
#Remove schools with percentages greater than 100 and look only at the year 2019. 
chronic_absenteeism <- chronic_absenteeism %>% filter(pct <= 1.00, year == "2019")



#Create a new column for just the third character in the original agency code. If it's a letter, we will know this is a charter school. Then filter for all the columns where that third character is a NUMBER. This will give us all the rows that ARE NOT charter schools. 

chronic_absenteeism <- chronic_absenteeism %>% mutate(charter_or_lea = 
 str_sub(chronic_absenteeism$district_code,3)) %>% filter(charter_or_lea == "1" | charter_or_lea == "2"| charter_or_lea =="3"| charter_or_lea =="4" | charter_or_lea == "5" | charter_or_lea == "6" | charter_or_lea == "7" | charter_or_lea == "8" | charter_or_lea == "9"| charter_or_lea == "0") 


#Filter out alternative schools. We are not using a very reputable site for this right now, but we will find a better one. 

chronic_absenteeism <-chronic_absenteeism %>% filter(agency_code != "910368",agency_code != "260374" ,agency_code != "040305",agency_code != "550308",agency_code != "770342",agency_code != "530306", agency_code != "160309",agency_code != "650355", agency_code != "300306",agency_code != "60U000", agency_code != "110303", agency_code != "630330", agency_code != "920381", agency_code != "880320",  agency_code != "320322", agency_code != "140306", agency_code != "700310", agency_code != "120308", agency_code != "450343" , agency_code != "260413" , agency_code != "470342" ,agency_code != "650354" , agency_code != "340427" , agency_code != "650345" ,agency_code != "320341" ,agency_code != "540318" , agency_code != "340385" , agency_code != "850324" , agency_code != "980306" ,agency_code != "620310" ,agency_code != "920508" ,
agency_code != "491305"  , agency_code != "241312" , agency_code != "200322" , agency_code != "680335" , agency_code != "130333" , agency_code != "490350" , agency_code != "410534" ,agency_code != "010378" , agency_code != "810368" , agency_code != "190310" , agency_code != "410533" ,agency_code != "920556" , agency_code != "790392" ,agency_code != "830316" , agency_code != "900365" , agency_code != "840370" ,agency_code != "430345" , agency_code != "640340" ,agency_code != "600439" ,agency_code != "230330" , agency_code != "560350" ,agency_code != "360372" ,agency_code != "530358" ,agency_code != "460488" , agency_code != "990340")

```



#What is the average rate of chronic absenteeism for all disabled students)
```{r}
#Get rid of scientific notation
options(scipen=999)

#Make a dataframe just for disabled chronic absenteeism rates in 2019 & make the count header lowercase. Get rid of schools that don't have disabled students. 
disabled_chronic_absenteeism <- chronic_absenteeism %>% filter(subgroup == "disabled", year == "2019",!is.na(pct)) %>% rename(count = Count)

#Find the total number of chronically absent disabled students. This will help weight the average. 
sum(disabled_chronic_absenteeism$count)

#Make a new column for weights & weight mulitiplied by percent & get rid of columns that we don't need
disabled_chronic_absenteeism <- disabled_chronic_absenteeism %>% mutate(weight = count/82775) %>% mutate(weight_times_percent = `weight`*`pct`) %>% select(year,agency_code,district_code,count,den,pct,weight, weight_times_percent) 


#Calculate the weighted average
sum(disabled_chronic_absenteeism$weight_times_percent)/sum(disabled_chronic_absenteeism$weight)
#The answer is 3.96 perent. 

#How many disabled students are there total?
sum(disabled_chronic_absenteeism$den)

```

#Text: 82,775 of North Carolina's disabled students are chronically absent. On average, 3.6 percent of a school's disabled students will be chronically absent. 



#Now see which schools strayed furthest from this average. 
```{r}
#Make a dataframe with a more limited set of columns that will allow you to see which school's & school districts strayed furthest from the average. Did they have a lot of disabled students?

chronic_disabled_ratio <- disabled_chronic_absenteeism %>%  mutate(average_percentage =0.03962896, ratio = pct/0.03962896) %>% select(agency_code,district_code,count,pct,average_percentage,ratio)

#How many schools had disabled students?
str(chronic_disabled_ratio)
#2,375 schools

#Now arrange the dataframe in descending order according to the ratio column. This will show you which individual schools strayed furthest from the average. 
worst_ratios <- chronic_disabled_ratio %>% arrange(desc(ratio)) %>% filter(ratio >= 2.00)
best_ratios <- chronic_disabled_ratio %>% arrange(ratio) %>% filter(ratio <= 0.5)

#71 out of 2,375 schools had rates of chronic absenteeism at least twice as high as the average percentage.That's about 2.99 percent of schools. 
```
About 3 percent of schools had rates of chronic absenteeism at least twice as high as the state's average percentage. 
```{r}

```




#Checking things out by district & average percentage.  
```{r}

#Now using the district_code column, let's find out if those schools are heavily concentrated in a particular county or counties. 
worst_ratios %>% group_by(district_code) %>% summarize(ratio = n()) %>% arrange(desc(ratio))

#33 of these schools are concentrated in 10 districts. About 28.7 percent 


#Now using the district_code column, let's find out if those schools are heavily concentrated in a particular county or counties. 
best_ratios %>% group_by(district_code) %>% summarize(ratio = n()) %>% arrange(desc(ratio))
```


#Checking things out by district and actual count of chronically absent students
```{r}
#Now using the district_code column, let's find out if those schools are heavily concentrated in a particular county or counties. 
 worst_ratios %>% group_by(district_code) %>% summarize(count = sum(count)) %>% arrange(desc(count)) 



```







