---
title: "disabled students & chronic absenteeism"
author: "Ellie "hacker(wo)man supreme" Heffernan"
date: "10/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Load in the data & load packages you will need. 
```{r}
library(readr)
library(lubridate)
library(tidyverse)
library(stringr)
library(ggplot2)
chronic_absenteeism <- read_csv("chronic_absenteeism.csv")
View(chronic_absenteeism)

chronic_absenteeism %>% filter(year == "2019",subgroup == "ALL")
```


#The Agency code's first three digits refer to the school district. The second three refer to the school itself. I want to create a new column that will just show what district the school is. I will use stringr to split the agency_code column in two & make a new column 

```{r}
chronic_absenteeism <-chronic_absenteeism %>% mutate(district_code = str_sub(chronic_absenteeism$agency_code,1,3))
  
  
```


#KC Elander recommended we remove all schools with percentages greater than 100, all charter schools, and all alternative schools.These schools enroll students later in the year, but they take their "count" data earlier. This is why they may have 400 chronically absent students and only 200 students enrolled. Many of those 400 students may have enrolled later. The data is flawed in this sense, and we should mention it in the story.  Phew. Time for some data cleaning.
```{r}
#Remove schools with percentages greater than 100 and look only at the year 2019. 
chronic_absenteeism <- chronic_absenteeism %>% filter(pct <= 1.00, year == "2019")



#Create a new column for just the third character in the original agency code. If it's a letter, we will know this is a charter school. Then filter for all the columns where that third character is a NUMBER. This will give us all the rows that ARE NOT charter schools. 

chronic_absenteeism <- chronic_absenteeism %>% mutate(charter_or_lea = 
 str_sub(chronic_absenteeism$district_code,3)) %>% filter(charter_or_lea == "1" | charter_or_lea == "2"| charter_or_lea =="3"| charter_or_lea =="4" | charter_or_lea == "5" | charter_or_lea == "6" | charter_or_lea == "7" | charter_or_lea == "8" | charter_or_lea == "9"| charter_or_lea == "0") 


#Filter out alternative schools. We are not using a very reputable site for this right now, but we will find a better one. 

chronic_absenteeism <-chronic_absenteeism %>% filter(agency_code != "910368",agency_code != "260374" ,agency_code != "040305",agency_code != "550308",agency_code != "770342",agency_code != "530306", agency_code != "160309",agency_code != "650355", agency_code != "300306",agency_code != "60U000", agency_code != "110303", agency_code != "630330", agency_code != "920381", agency_code != "880320",  agency_code != "320322", agency_code != "140306", agency_code != "700310", agency_code != "120308", agency_code != "450343" , agency_code != "260413" , agency_code != "470342" ,agency_code != "650354" , agency_code != "340427" , agency_code != "650345" ,agency_code != "320341" ,agency_code != "540318" , agency_code != "340385" , agency_code != "850324" , agency_code != "980306" ,agency_code != "620310" ,agency_code != "920508" ,
agency_code != "491305"  , agency_code != "241312" , agency_code != "200322" , agency_code != "680335" , agency_code != "130333" , agency_code != "490350" , agency_code != "410534" ,agency_code != "010378" , agency_code != "810368" , agency_code != "190310" , agency_code != "410533" ,agency_code != "920556" , agency_code != "790392" ,agency_code != "830316" , agency_code != "900365" , agency_code != "840370" ,agency_code != "430345" , agency_code != "640340" ,agency_code != "600439" ,agency_code != "230330" , agency_code != "560350" ,agency_code != "360372" ,agency_code != "530358" ,agency_code != "460488" , agency_code != "990340")

chronic_absenteeism %>% filter(year == "2019",subgroup == "ALL")
```



#What is the average rate of chronic absenteeism for all disabled students)
```{r}
#Get rid of scientific notation
options(scipen=999)

#Make a dataframe just for disabled chronic absenteeism rates in 2019 & make the count header lowercase. Get rid of schools that don't have disabled students. 
disabled_chronic_absenteeism <- chronic_absenteeism %>% filter(subgroup == "disabled", year == "2019",!is.na(pct)) %>% rename(count = Count)

#Find the total number of chronically absent disabled students. This will help weight the average. 
total_chronically_absent_disabled_students <- sum(disabled_chronic_absenteeism$count)

#Make a new column for weights & weight mulitiplied by percent & get rid of columns that we don't need
disabled_chronic_absenteeism <- disabled_chronic_absenteeism %>% mutate(weight = count/total_chronically_absent_disabled_students) %>% mutate(weight_times_percent = `weight`*`pct`) %>% select(year,agency_code,district_code,count,den,pct,weight, weight_times_percent) 


#Calculate the weighted average
sum(disabled_chronic_absenteeism$weight_times_percent)/sum(disabled_chronic_absenteeism$weight)
#The answer is 3.96 perent. 

#How many disabled students are there total?
sum(disabled_chronic_absenteeism$den)

total_chronically_absent_disabled_students
```

#Text: 82,775 of North Carolina's disabled students are chronically absent. On average, 3.6 percent of a school's disabled students will be chronically absent. 



#Now see which schools strayed furthest from this average. 
```{r}
#Make a dataframe with a more limited set of columns that will allow you to see which schools & school districts strayed furthest from the average. Did they have a lot of disabled students?

chronic_disabled_ratio <- disabled_chronic_absenteeism %>%  mutate(average_percentage =0.03962896, ratio = pct/0.03962896) %>% select(agency_code,district_code,count,pct,average_percentage,ratio)

#How many schools had disabled students?
str(chronic_disabled_ratio)
#2,375 schools

#Now arrange the dataframe in descending order according to the ratio column. This will show you which individual schools strayed furthest from the average. 
worst_ratios <- chronic_disabled_ratio %>% arrange(desc(ratio)) %>% filter(ratio >= 2.00)
best_ratios <- chronic_disabled_ratio %>% arrange(ratio) %>% filter(ratio <= 0.5)
```
#Text: 71 out of 2,375 schools had rates of chronic absenteeism at least twice as high as the average percentage.That's about 2.99 percent of schools. 743 schools had rates of chronic absenteeism that were half the size of the average percentage. That's about 31.2 percent. 



#Checking things out by district & average percentage.  
```{r}

#Now using the district_code column, let's find out if those schools are heavily concentrated in a particular county or counties. 
worst_districts <- worst_ratios %>% group_by(district_code) %>% summarize(agency_code = n()) %>% arrange(desc(agency_code)) %>% rename(number_of_bad_schools = agency_code)

#33 of these schools are concentrated in 10 districts. About 28.7 percent 


#Now using the district_code column, let's find out if those schools are heavily concentrated in a particular county or counties. 
best_districts <- best_ratios %>% group_by(district_code) %>% summarize(agency_code = n()) %>% arrange(desc(agency_code)) %>% rename(number_of_good_schools = agency_code)




```
#Text: 33 of the 71 worst ratio schools are concentrated in 10 districts. That's about 46.47 percent of the worst schools concentrated in 8.70 percent of the districts. 48.2 percent of the best schools are in 10 districts. Clearly things are very segregated. 

#Now let's see if certain school districts have the highest or lowest numbers of chronically absent disabled students. 
```{r}
#Looking at worst ratio schools 
 worst_ratios %>% group_by(district_code) %>% summarize(count = sum(count)) %>% arrange(desc(count))

#Looking at best ratio schools
best_ratios %>% group_by(district_code) %>% summarize(count = sum(count)) %>% arrange(count)

#1,545 of North Carolina's chronically absent disabled students are concentrated in 10 districts. There are 82,775 chronically absent disabled students in total. That's only 1.87 percent. 
```

#Text: 1,545 of North Carolina's chronically absent disabled students are concentrated in 10 districts. There are 82,775 chronically absent disabled students in total. That's only 1.87 percent.


#Find each district's average rate of chronic absenteeism
```{r}
district_average_rates <- disabled_chronic_absenteeism %>% group_by(district_code) %>% summarise(average_pct = (sum(weight_times_percent))/(sum(weight))) %>% arrange(desc(average_pct))
```

#How many disabled students per district
```{r}
disabled_count <- disabled_chronic_absenteeism %>% filter(year == 2019) %>% group_by(district_code) %>% summarise(sum(den)) 

left_join(disabled_count,for_joins)


 

```



#Spending per disabled student (The numbers in parentheses are from financial data we have in complicated excel file that will not scrape to R.The second number is the number of disabled students in a district. This was us manuallly calculating spending per capita.)
```{r}
#1 Charlotte-Mecklenburg
( 66565775 + 1475779) /285122 
89	
#2 Newton Conover
 (1849974+ 692575)/5446

0
#3 Winston Salem (Forsyth County)
 (33850264 + 1578326)/ 1578326 

20

#4 Guilford
 45490081/137452
 
 51
#5 Rutherford
  (5529712+ 97398)/15162
 4
 
#6 Cumberland
  (30977388+ 193962)/97240
 
26	
 #7 Lexington City
  (1964009+ 261066)/5946
1	
 
 #8 Lee County
  (5687979+ 235964)/17783
 3	
 #9 Granville County
  (5063308+ 9177)/13256
 0
 
 #10 Wayne County
  (11534710 +  593943)/34834
 8	

 
 
 #------------------------
#1 Clinton City 
989917/5872
 
 0

#2 Roanoake Rapids City
1835268/5450

0

#3 Greene County Schools
(1328174+ 37152) /5472

0

#4 Elkin City Schools
(762125+ 38181)/2342

0
#5 Alleghany County Schools
 (940347 + 40164)/2664

1
#6 Camden County Schools
 (1134131 +15863)/3348

1

#7 Caswell County Schools
 (1599346+ 56118)/4850	

1 
#8 Duplin County Schools
 4202750/18486
 
 4
#9 Martin County Schools
  (2113950+ 298218) /5796
 
 2
 
 #10 Thomasville City
  1426953/4508	
  1
```


 6129317/24588


















