---
title: "Mapping"
author: "Ellie "hacker(wo)man supreme" Heffernan"
date: "10/27/2020"
output: html_document
---
#Load in the shape file and packages you will need.  
```{r}

#Packages
library(tigris)
options(tigris_use_cache = TRUE)
library(ggplot2)
library(tidyverse)
library(sf)
library(leaflet)
#Shape file 
getwd()
fifty_location <-"/Users/ephmd920/Documents/MEJO 390/HMWK92/cb_2018_us_state_20m/cb_2018_us_state_20m.shp"

fifty_states <-st_read(fifty_location)
```


#Get the North Carolina shape file. 
```{r}
options(tigris_class ="sf")
#Anything loaded can only be a shapefile. 

nc_school_districts <-school_districts("NC",cb=T)


```

#Plot this out
```{r}
nc_school_districts_map <- ggplot(nc)+geom_sf()+theme_void()+theme(panel.grid.major=element_line(color="transparent"))+labs(title="North Carolina school districts")
```


#Join the chronic disabled ratio & for joins dataframes. This will give you the name of the district & the district code.Then join this dataframe to the shapefile. 
```{r}
district_average_rates <- left_join(district_average_rates,for_joins)

mapping_district_rates <-left_join(nc_school_districts,district_average_rates,by=c("NAME"="district_name"))



```


#MAP!!
```{r}
ggplot(mapping_district_rates) + geom_sf(aes(fill=average_pct))+ 
scale_fill_distiller(direction =1,palette ="Greens",name="Rates")+labs(title="Average rates of chronic absenteeism",caption ="Source:North Carolina Department of Public Instruction")



```
#I think making this an interactive map would be better. Time to use leaflet!
```{r}
nc_school_districts %>% leaflet() %>% addTiles()%>%
  addPolygons(popup =~NAME)
```


#Create a color palette that shows the full "range" of numbers
```{r}
pal <- colorNumeric("Reds",domain = mapping_district_rates$average_pct)


```



#Time to map!
```{r}

#Creating pop-up text
popup_nc_school_districts <-paste0(as.character(mapping_district_rates$NAME), "</br>")
popup_nc_school_districts <- paste0(popup_nc_school_districts,as.character(str_sub(mapping_district_rates$average_pct),1,3))


#Actually making the map 
leaflet() %>% addProviderTiles("CartoDB.Positron") %>% setView(-79.483330,35.712046,zoom=6.5) %>% addPolygons(data=mapping_district_rates,fillColor = pal(mapping_district_rates$average_pct), fillOpacity = .7,weight = .2,smoothFactor = .2,popup = ~popup_nc_school_districts) %>% addLegend(pal = pal,values=mapping_district_rates$average_pct,position = "bottomright",title = "Average <br/> Rate of <br/> Chronic <br/> Absenteeism")
```


#Some schools are NA due to slight miss-spellings. We'll use open refine. To change the values in the distric_average_rates dataframe. 
```{r}
#First, export that dataframe 
write.csv(district_average_rates,"district_average_rates.csv")

#Load the revised dataframe
district_average_rates <- read_csv("~/Downloads/district_average_rates-csv.csv")



```



#Create a color palette for the new map. 
```{r}
pal <- colorNumeric("Reds",domain = mapping_district_disabled_pcts_range$average_pct)


```



#Time to map!
```{r}
#Creating pop-up text
popup_nc_school_districts <-paste0(as.character(mapping_district_rates$NAME), "</br>")
popup_nc_school_districts <- paste0(popup_nc_school_districts,as.character(str_sub(mapping_district_rates$average_pct),1,3))


#Actually making the map 
leaflet() %>% addProviderTiles("CartoDB.Positron") %>% setView(-79.483330,35.712046,zoom=6.5) %>% addPolygons(data=mapping_district_rates,fillColor = pal(mapping_district_rates$average_pct), fillOpacity = .7,weight = .2,smoothFactor = .2,popup = ~popup_nc_school_districts) %>% addLegend(pal = pal,values=mapping_district_rates$average_pct,position = "bottomright",title = "Average <br/> Rate of <br/> Chronic <br/> Absenteeism")
```


#I'm going to make another map showing districts' ranges of chronic absenteeism rates. We'll have a similar problem with name differences. So let's start with open refine.

```{r}
#Write the new csv. 
write.csv(district_disabled_pcts_range,"district_disabled_pcts_rates.csv")

#Import the new dataframe 
district_disabled_pcts_range<- read_csv("~/Downloads/district_disabled_pcts_rates-revised.csv")
View(district_disabled_pcts_rates_revised)

#First join the districts_disabled_pcts_ranges dataframe with the for_joins dataframe. This will let us see the names of districts instead of just numbers!
district_disabled_pcts_range <- left_join(district_disabled_pcts_range,for_joins)

#Now join it in with the shapefile!
mapping_district_disabled_pcts_range <- left_join(nc_school_districts,district_disabled_pcts_range,by=c("NAME"="district_name"))


```

#Create a new palette
```{r}
pal2 <- colorNumeric("Greens",domain = mapping_district_disabled_pcts_range$range)
```

#Now map this 
```{r}
#Creating pop-up text
popup_school_ranges <-paste0(as.character(mapping_district_disabled_pcts_range$NAME), "</br>")
popup_school_ranges <- paste0(popup_school_ranges,as.character(mapping_district_disabled_pcts_range$range))


#Actually making the map 
leaflet() %>% addProviderTiles("CartoDB.Positron") %>% setView(-79.483330,35.712046,zoom=6.5) %>% addPolygons(data=mapping_district_disabled_pcts_range,fillColor = pal2(mapping_district_disabled_pcts_range$range), fillOpacity = .7,weight = .2,smoothFactor = .2,popup = ~popup_school_ranges) %>% addLegend(pal = pal2,values=mapping_district_disabled_pcts_range$range,position = "bottomright",title = "Range of <br/> Rates of <br/> Chronic <br/> Absenteeism <br/> (Percentage Points)")
```


























































































