---
title: "Mapping"
author: "Ellie "hacker(wo)man supreme" Heffernan"
date: "10/27/2020"
output: html_document
---
#Load in the shape file and packages you will need.  
```{r}

#Packages
library(tigris)
options(tigris_use_cache = TRUE)
library(ggplot2)
library(tidyverse)
library(sf)
#Shape file 
getwd()
fifty_location <-"/Users/ephmd920/Documents/MEJO 390/HMWK92/cb_2018_us_state_20m/cb_2018_us_state_20m.shp"

fifty_states <-st_read(fifty_location)
```


#Get the North Carolina shape file. 
```{r}
options(tigris_class ="sf")
#Anything loaded can only be a shapefile. 

nc_school_districts <-school_districts("NC",cb=T)


```

#Plot this out
```{r}
nc_school_districts_map <- ggplot(nc)+geom_sf()+theme_void()+theme(panel.grid.major=element_line(color="transparent"))+labs(title="North Carolina school districts")
```


#Join the chronic disabled ratio & for joins dataframes. This will give you the name of the district & the district code.Then join this dataframe to the shapefile. 
```{r}
district_average_rates <- left_join(district_average_rates,for_joins)

mapping_district_rates <-left_join(nc_school_districts,district_average_rates,by=c("NAME"="district_name"))



```

?left_join
#MAP!!
```{r}
ggplot(mapping_district_rates) + geom_sf(aes(fill=average_pct))+ 
scale_fill_distiller(direction =1,palette ="Greens",name="Rates")+labs(title="Average rates of chronic absenteeism",caption ="Source:North Carolina Department of Public Instruction")



```
#I think making this an interactive map would be better. Time to use leaflet!
```{r}
nc_school_districts %>% leaflet() %>% addTiles()%>%
  addPolygons(popup =~NAME)
```


#Create a color palette that shows the full "range" of numbers
```{r}
pal <- colorNumeric("Reds",domain = mapping_district_rates$average_pct)


```



#Time to map!
```{r}

#Creating pop-up text
popup_nc_school_districts <-paste0(as.character(mapping_district_rates$NAME), "</br>")
popup_nc_school_districts <- paste0(popup_nc_school_districts,as.character(str_sub(mapping_district_rates$average_pct),1,3))


#Actually making the map 
leaflet() %>% addProviderTiles("CartoDB.Positron") %>% setView(-79.483330,35.712046,zoom=6.5) %>% addPolygons(data=mapping_district_rates,fillColor = pal(mapping_district_rates$average_pct), fillOpacity = .7,weight = .2,smoothFactor = .2,popup = ~popup_nc_school_districts) %>% addLegend(pal = pal,values=mapping_district_rates$average_pct,position = "bottomright",title = "Average <br/> Rate of <br/> Chronic <br/> Absenteeism")
```


#Some schools are NA due to slight miss-spellings. We'll use open refine. To change the values in the distric_average_rates dataframe. 
```{r}
#First, export that dataframe 
write.csv(district_average_rates,"district_average_rates.csv")

#Load the revised dataframe
district_average_rates <- read_csv("~/Downloads/district_average_rates-csv.csv")



```

#Copy and PASTE EVERYTHING after the creation of the district_average_rates dataframe
```{r}
mapping_district_rates <-left_join(nc_school_districts,district_average_rates,by=c("NAME"="district_name"))
```


#MAP!!
```{r}
ggplot(mapping_district_rates) + geom_sf(aes(fill=average_pct))+ 
scale_fill_distiller(direction =1,palette ="Greens",name="Rates")+labs(title="Average rates of chronic absenteeism",caption ="Source:North Carolina Department of Public Instruction")



```
#I think making this an interactive map would be better. Time to use leaflet!
```{r}
nc_school_districts %>% leaflet() %>% addTiles()%>%
  addPolygons(popup =~NAME)
```


#Create a color palette that shows the full "range" of numbers
```{r}
pal <- colorNumeric("Reds",domain = mapping_district_rates$average_pct)


```



#Time to map!
```{r}
#Creating pop-up text
popup_nc_school_districts <-paste0(as.character(mapping_district_rates$NAME), "</br>")
popup_nc_school_districts <- paste0(popup_nc_school_districts,as.character(str_sub(mapping_district_rates$average_pct),1,3))


#Actually making the map 
leaflet() %>% addProviderTiles("CartoDB.Positron") %>% setView(-79.483330,35.712046,zoom=6.5) %>% addPolygons(data=mapping_district_rates,fillColor = pal(mapping_district_rates$average_pct), fillOpacity = .7,weight = .2,smoothFactor = .2,popup = ~popup_nc_school_districts) %>% addLegend(pal = pal,values=mapping_district_rates$average_pct,position = "bottomright",title = "Average <br/> Rate of <br/> Chronic <br/> Absenteeism")
```



#Now let's do this with funding. 

#Join the teacher_supplements dataframe to the shapefile. 
```{r}
mapping_teacher_supplements <-left_join(nc_school_districts,teacher_supplements,by=c("NAME"="district_name"))



```


#Create a color palette that shows the full "range" of numbers
```{r}
pal <- colorNumeric("Reds",domain = mapping_teacher_supplements$average_teacher_supplement)


```



#Time to map!
```{r}
#Creating pop-up text
popup_nc_school_districts2 <-paste0(as.character(mapping_teacher_supplements$NAME), "</br> $")
popup_nc_school_districts2 <- paste0(popup_nc_school_districts2,as.character(mapping_teacher_supplements$average_teacher_supplement))



#Actually making the map 
leaflet() %>% addProviderTiles("CartoDB.Positron") %>% setView(-79.483330,35.712046,zoom=6.5) %>% addPolygons(data=mapping_teacher_supplements,fillColor = pal(mapping_teacher_supplements$average_teacher_supplement), fillOpacity = .7,weight = .2,smoothFactor = .2,popup = ~popup_nc_school_districts2) %>% addLegend(pal = pal,values=mapping_teacher_supplements$average_teacher_supplement,position = "bottomright",title = "Average <br/> Annual  <br/> Teacher <br/> Supplement")
```





#Now do this for PPE without nutrition 
```{r}
mapping_ppe_without_nutrition <-left_join(nc_school_districts,ppe_without_nutrition,by=c("NAME"="district_name"))
```


#Create a color palette that shows the full "range" of numbers
```{r}
pal <- colorNumeric("Reds",domain = mapping_ppe_without_nutrition$total_ppe)


```





#Time to map!
```{r}
#Creating pop-up text
popup_nc_school_districts3 <-paste0(as.character(mapping_ppe_without_nutrition$NAME), "</br> $")
popup_nc_school_districts3 <- paste0(popup_nc_school_districts3,as.character(mapping_ppe_without_nutrition$total_ppe))



#Actually making the map 
leaflet() %>% addProviderTiles("CartoDB.Positron") %>% setView(-79.483330,35.712046,zoom=6.5) %>% addPolygons(data=mapping_ppe_without_nutrition,fillColor = pal(mapping_ppe_without_nutrition$total_ppe), fillOpacity = .7,weight = .2,smoothFactor = .2,popup = ~popup_nc_school_districts3) %>% addLegend(pal = pal,values=mapping_ppe_without_nutrition$total_ppe,position = "bottomright",title = "Average <br/> Annual  <br/> Teacher <br/> Supplement")
```



































